Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-06-04 analysis/paper/paper.Rmd
Edits to interrater repeatability differences analysis

The articles' computational reproducibility were analysed using Bayesian mixed-effect models fit using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] to evaluate the fixed effects of the publication (journal title), five-year journal impact factor, journal open access policy, journal data and code deposition instructions on three factors, data, code and software availability.
The models included 'year', 'journal' and 'assignee' as random effects except in the year of publication analysis where 'year' was a fixed effect, publication analysis where the 'journal' was a fixed effect and five-year impact factor where correlations between the journal title and impact factor affected the software availability model.

>>>>

The articles' scores for data, code and software availability were analysed using Bayesian mixed-effect models fit using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] to evaluate the fixed effects of the publication (journal title), five-year journal impact factor, year of publication, journal open access policy, and the effect of the availability of the software used, `software_avail` on the code and data availability.
The models included 'year', 'journal' and 'assignee' as random effects except in the year of publication analysis where 'year' was a fixed effect, journal title analysis where the 'journal' was a fixed effect and the five-year impact factor model where correlations between the journal title and impact factor affected the software availability model.
